\huge A Usability Evaluation of Tor Launcher

### 2016-10-21 pets2017-paper/pets2017-paper.tex
new title.
create procedure subsections, mark things to do.

  \title{\huge A Better (One-Line!) Title Here}

  \runningtitle{A Better (One-Line!) Title Here}

@@

  \begin{abstract}
{
We evaluate, design, and test the Tor Launcher interface by
placing users in simulated censorship environments, instructing them to use Tor
to circumvent censorship, and measuring their interface interactions.
A 16-participant qualitative study examines user assumptions and common mistakes.
We use the results as feedback to redesign the configuration interface.
A 114-participant quantitative study shows that our design changes result in
a significant reduction in time. We conclude with recommendations for changes 
to the current interface as well as alternative solutions.}
\end{abstract}
  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

@@

\section{Usability Inspection}
{\color {red}
We used a combination of usability inspection methods~\cite{nielsen1994usability}
to prepare for the user study. Two researchers conducted a pluralistic 
walkthrough and stepped through various censorship
scenarios, discussing which elements would be involved for that use case, and walking 
through the configuration process. After compiling all the possible paths through the 
interface, researchers performed feature inspection, listing sequences of features used 
to accomplish typical tasks and taking note of long sequences or cumbersome
steps. In addition, we performed a heuristic evaluation to mark
likely causes of confusion for users during our study.
}

>>>>

  \title{\huge A Usability Evaluation of Tor Launcher}

  \runningtitle{A Usability Evaluation of Tor Launcher}

@@

  \begin{abstract}
{
{\color {blue}
We evaluate, design, and test the Tor Launcher interface by
placing users in simulated censorship environments, instructing them to use Tor
to circumvent censorship, and measuring their interface interactions.
A 16-participant qualitative study examines user assumptions and common mistakes.
We use the results as feedback to redesign the configuration interface.
A 114-participant quantitative study shows that our design changes result in
a significant reduction in time. We conclude with recommendations for changes 
to the current interface as well as alternative solutions.
}
}
\end{abstract}
  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

%We used a combination of usability inspection methods~\cite{nielsen1994usability}
%to prepare for the user study. Two researchers conducted a pluralistic 
%walkthrough and stepped through various censorship
%scenarios, discussing which elements would be involved for that use case, and walking 
%through the configuration process. After compiling all the possible paths through the 
%interface, researchers performed feature inspection, listing sequences of features used 
%to accomplish typical tasks and taking note of long sequences or cumbersome
%steps. In addition, we performed a heuristic evaluation to mark
%likely causes of confusion for users during our study.

@@

\section{Usability Inspection}
{\color {blue}
Short intro sentence. 
}

\subsection{Procedure} 
{\color {blue}
David and I sat down in the same room, started from the first screen, and tried to toggle every single path in a systematic way, usually going with the default option first if any, then working from top to bottom.
}

\subsection{Observations}
{\color {blue}
Quick refer to the digraph, and explain everything in the caption. Put end states in the appendix (if it doesn't fit in the caption.

A short paragraph with 1-3 observations--using a non-leading tone! 
}
